Tempo and mode of promoter evolution as observed in the \textit{Paramecium aurelia} species complex

### 2020-07-31 manuscript.tex
More additions to introduction

Interestingly, while the fates of ortho-paralog pairs that arise through whole genome duplication (WGD) has been heavily studied (enter citations for \citep{Ohno:1970wm}; Wolfe and Shields, 1997, Force et al., 1999, others), the behavior of \textit{cis}-regulatory regions of duplicate gene pairs is less well-understood. (Add a bit about paralogs and how we can use them to help us understand how \textit{cis}-regulatory regions evolve. -> we haven't studied the fate of cis-regulatory regions in ortho-paralog pairs.) then:
-Add a paragraph introducing the Paramecium system -> the experiment\\
-Final sentence(s) of intro: what we found plus the novelty eg this is the first study of its kind to do x.

>>>>

Duplicate genes are a major source of evolutionary change (cite Moore and Puruggnan, 2006), and their evolutionary fates have long been a subject of intense study (cite several revent studies). The availability of high-quality genome assemblies and genome annotations has allowed us to investigate duplicate gene evolution in a variety of phylogenetic contexts (cite Gu et al., 2003 and others). However, while the fates of ortho-paralog pairs that arise through whole genome duplication (WGD) has been heavily studied (enter citations for \citep{Ohno:1970wm}; Wolfe and Shields, 1997, Force et al., 1999, others), the fates of \textit{cis}-regulatory regions of duplicate gene pairs is much less well-understood. (Discuss Haberer et al., Dong et al and Arsovski et al).

(Add a bit about paralogs and how we can use them to help us understand how \textit{cis}-regulatory regions evolve. then:
-Add a paragraph introducing the Paramecium system -> the experiment\\
-Final sentence(s) of intro: what we found plus the novelty eg this is the first study of its kind to do x.
